We will now focus our discussion on the act of a purchase with invariant risk. According to the Risk Invariance theorem
(\ref{riskinv}), if $Alice$ wants to buy something that costs $V$ from the vendor $Bob$, she should first find a new
distribution of her outgoing direct trust such that $maxFlow'\left(Alice, Bob\right) = maxFlow\left(Alice, Bob\right) - V$ and
then directly entrust $V$ to $Bob$. The theorem then ensures that the initial risk (i.e indirect trust) from $Alice$ to $Bob$
is equal to the final. In the following section we discuss several algorithms that calculate possible new distributions for
$Alice$'s outgoing direct trust. The direct trust will be referred to as capacity, because of the maximum flow context.

Let $A \in \mathcal{V}$ source, $B \in \mathcal{V}$ sink. For the following, we suppose that $\mathcal{G}$ is the current
graph and $A$ is currently deciding $\mathcal{G}'$. We use the following notation:
\begin{align*}
  C \mbox{ capacity configuration with } c_{Av} &= DTr_{\mathcal{G}, A \rightarrow v} \\
  C' \mbox{ capacity configuration with } c'_{Av} &= DTr_{\mathcal{G}', A \rightarrow v}
\end{align*}

We will use the following notation for clarity:
\begin{equation*}
\begin{gathered}
  \begin{cases}
    X = MaxFlow_{\mathcal{G}}\left(A, B\right) \\
    X' = MaxFlow_{\mathcal{G}'}\left(A, B\right)
  \end{cases}, \mbox{ for some } MaxFlow \mbox{ execution} \\
  \begin{cases}
    F = maxFlow_{\mathcal{G}}\left(A, B\right) \\
    F' = maxFlow_{\mathcal{G}'}\left(A, B\right)
  \end{cases}
\end{gathered}
\end{equation*}
Any subscripts or superscripts applied to $X$ and $F$ refer to the capacity configuration with the exact same subscripts and
superscripts.

Furthermore, we suppose an arbitrary ordering of the members of $N^{+}\left(A\right)$. We set $n = |N^{+}\left(A\right)|$.
Thus
\begin{equation*}
  N^{+}\left(A\right) = \{v_1, ..., v_n\}
\end{equation*}
We use these subscripts to refer to the respective capacities (a.k.a. direct trusts) and flows. Thus
\begin{equation*}
  \begin{array}{l}
    x_i = x_{Av_i} \enspace, \\
    c_i = c_{Av_i} \enspace,
  \end{array}
  \mbox{ where } i \in [n]
\end{equation*}
There is no difference in the capacities that are not outgoing from $A$ between the graphs $\mathcal{G}$ and $\mathcal{G}'$,
since $A$ can only modify the capacities outgoing from herself.
