We will now focus our discussion on the act of a purchase with invariant risk. Suppose the game is currently depicted by graph
$\mathcal{G}$ and after the necessary preparations for paying with invariant risk, the game corresponds to graph
$\mathcal{G}'$. According to the Risk Invariance theorem \cite{trustisrisk}, if $Alice$ wants to buy something that costs $V$
from the vendor $Bob$, she should first find a new distribution of her outgoing direct trust such that
$maxFlow_{\mathcal{G}'}\left(Alice, Bob\right) = maxFlow_{\mathcal{G}}\left(Alice, Bob\right) - V$ and then directly entrust
$V$ to $Bob$. The theorem then ensures that the initial risk (i.e indirect trust) from $Alice$ to $Bob$ is equal to the final.
In the current section we discuss several algorithms that calculate possible new distributions for $Alice$'s outgoing direct
trust. The direct trust will be referred to as capacity, because of the maximum flow context.

Let $A \in \mathcal{V}$ source, $B \in \mathcal{V}$ sink. We use the following notation:
\begin{align*}
  C \mbox{ capacity configuration with } c_{Av} &= DTr_{\mathcal{G}, A \rightarrow v} \\
  C' \mbox{ capacity configuration with } c'_{Av} &= DTr_{\mathcal{G}', A \rightarrow v}
\end{align*}

We will use the following notation for clarity:
\begin{equation*}
\begin{gathered}
  \begin{cases}
    X = MaxFlow_{\mathcal{G}}\left(A, B\right) \\
    X' = MaxFlow_{\mathcal{G}'}\left(A, B\right)
  \end{cases}, \mbox{ for some } MaxFlow \mbox{ execution} \\
  \begin{cases}
    F = maxFlow_{\mathcal{G}}\left(A, B\right) \\
    F' = maxFlow_{\mathcal{G}'}\left(A, B\right)
  \end{cases}
  \enspace.
\end{gathered}
\end{equation*}
Any subscripts or superscripts applied to $X$ and $F$ refer to the capacity configuration with the exact same subscripts and
superscripts.

Furthermore, we suppose an arbitrary ordering of the members of $N^{+}\left(A\right)$. We set $n = |N^{+}\left(A\right)|$.
Thus
\begin{equation*}
  N^{+}\left(A\right) = \{v_1, ..., v_n\} \enspace.
\end{equation*}
We use these subscripts to refer to the respective capacities and flows. Thus
\begin{equation*}
  \begin{array}{l}
    x_i = x_{Av_i} \enspace, \\
    c_i = c_{Av_i} \enspace,
  \end{array}
  \mbox{ where } i \in [n] \enspace.
\end{equation*}
There is no difference in the capacities that are not outgoing from $A$ between the graphs $\mathcal{G}$ and $\mathcal{G}'$,
since $A$ can only modify the capacities outgoing from herself.
