\section{Further Research}

  %\subsection{Trust Transfer Algorithms}
    When a purchase is made, outgoing direct trust must be reduced such that (\ref{primetrust}) holds. Trust redistribution
    algorithms for this will be discussed in a future paper.
    
  %\subsection{Dynamic Setting}
    Our game is static. In a future dynamic setting, users should be able to play simultaneously, freely join, depart or
    disconnect temporarily from the network. Other types of multisigs, such as 1-of-3, can be explored for the
    implementation of multi-party direct trust.

  %\subsection{Zero knowledge}
    MaxFlow in our case needs complete network knowledge, which can lead to privacy issues through deanonymisation
    techniques \cite{deanonymisation}. Calculating the flows in zero knowledge remains an open question.
    SilentWhispers \cite{silentwhispers} and its centralized predecessor, PrivPay \cite{privpay}, seem to offer invaluable
    insight into how privacy can be achieved.

  %\subsection{Game Theoretic Analysis}
    Our game theoretic analysis is simple. An interesting analysis would involve modelling repeated purchases with the
    respective edge updates on the trust graph and treating trust on the network as part of the utility function.

  %\subsection{Implementation and Experimental Results}
    An implementation as a wallet on any blockchain of our financial game is most welcome. A simulation or actual
    implementation of Trust Is Risk, combined with analysis of the resulting dynamics can yield interesting experimental
    results. Subsequently, our trust network can be used in other applications, such as decentralized social networks, an
    example of which is Synereo \cite{synereo}.

