\begin{thebibliography}{40}
  \bibitem{loc}
  Sanchez W.: Lines of Credit. \url{https://gist.github.com/drwasho/2c40b91e169f55988618#part-3-web-of-credit} (2016)
  \bibitem{bitcoin}
  Nakamoto S.: Bitcoin: A Peer-to-Peer Electronic Cash System (2008)
  \bibitem{masteringbitcoin}
  Antonopoulos A. M.: Mastering Bitcoin: Unlocking Digital Cryptocurrencies. O'Reilly Media, Inc. (2014)
  \bibitem{kmrs}
  Karlan D., Mobius M., Rosenblat T., Szeidl A.: Trust and social collateral. The Quarterly Journal of Economics, pp.
  1307-1361 (2009)
  \bibitem{clrs}
  Cormen T. H., Leiserson C. E., Rivest R. L., Stein C.: Introduction to Algorithms (3rd ed.). MIT Press and McGraw-Hill
  (2009)
  \bibitem{maxflownm}
  Orlin J. B.: Max Flows in O(nm) Time, or Better. STOC '13 Proceedings of the forty-fifth annual ACM symposium on Theory
  of computing, pp.765-774, ACM, New York, doi:10.1145/2488608.2488705 (2013)
  \bibitem{sybilattack}
  Douceur J. R.: The Sybil Attack. International workshop on Peer-To-Peer Systems (2002)
  \bibitem{pgp}
  Zimmermann P.: PGP Source Code and Internals. The MIT Press (1995)
  \bibitem{freenet}
  Clarke I., Sandberg O., Wiley B., Hong T. W.: Freenet: A Distributed Anonymous Information Storage and
  Retrieval System. H. Federrath, Designing Privacy Enhancing Technologies pp. 46-66, Berkeley, USA: Springer-Verlag
  Berlin Heidelberg (2001)
  \bibitem{pki}
  Adams C., Lloyd S.: Understanding PKI: concepts, standards, and deployment considerations. Addison-Wesley Professional
  (2003)
  \bibitem{bazaar}
  Post A., Shah V., Mislove A.: Bazaar: Strengthening User Reputations in Online Marketplaces. Proceedings of NSDI'11:
  8th USENIX Symposium on Networked Systems Design and Implementation, p. 183 (2011)
  \bibitem{byzantine}
  Lamport L., Shostak R., Pease M.: The Byzantine Generals Problem. ACM Transactions on Programming Languages and Systems
  (TOPLAS) 4.3, pp. 382-401 (1982)
  \bibitem{fire}
  Huynh T. D., Jennings N. R., Shadbolt N. R.: An Integrated Trust and Reputation Model for Open Multi-Agent Systems.
  Autonomous Agents and Multi-Agent Systems, 13(2), pp. 119-154 (2006)
  \bibitem{core}
  Michiardi P., Molva R.: Core: a Collaborative Reputation Mechanism to Enforce Node Cooperation in Mobile Ad-hoc
  Networks. Advanced Communications and Multimedia Security, pp. 107-121, Springer US (2002)
  \bibitem{openrep}
  Cannon L.: Open Reputation: the Decentralized Reputation Platform (2015)
  \url{https://openreputation.net/open-reputation-high-level-whitepaper.pdf}
  \bibitem{ghkkw}
  Gr\"unert A., Hudert S., K\"onig S., Kaffille S., Wirtz G.: Decentralized Reputation Management for Cooperating Software
  Agents in Open Multi-Agent Systems. ITSSA, 1(4), pp. 363-368 (2006)
  \bibitem{rk}
  Repantis T., Kalogeraki V.: Decentralized Trust Management for Ad-hoc Peer-to-Peer Networks. Proceedings of the 4th
  International Workshop on Middleware for Pervasive and Ad-hoc Computing, MPAC 2006, p. 6, ACM (2006)
  \bibitem{mui}
  Mui L., Mohtashemi M., Halberstadt A.: A Computational Model of Trust and Reputation. System Sciences, 2002. HICSS.
  Proceedings of the 35th Annual Hawaii International Conference, pp. 2431-2439 IEEE (2002)
  \bibitem{beta}
  J\o{}sang A., Ismail R.: The Beta Reputation System. Proceedings of the 15th Bled Electronic Commerce Conference (2002)
  \bibitem{pace}
  Suryanarayana G., Erenkrantz J. R., Taylor R. N.: An Architectural Approach for Decentralized Trust Management. IEEE
  Internet Computing, 9(6), pp. 16-23 (2005)
  \bibitem{vpc}
  Visan A., Pop F., Cristea V.: Decentralized Trust Management in Peer-to-Peer Systems. 10th International Symposium on
  Parallel and Distributed Computing, pp. 232-239, IEEE (2011)
  \bibitem{sdt}
  Suryanarayana G., Diallo M., Taylor R. N.: A Generic Framework for Modeling Decentralized Reputation-Based Trust Models.
  14th ACM SigSoft Symposium on Foundations of Software Engineering (2006)
  \bibitem{wot}
  Caronni G.: Walking the web of trust. Enabling Technologies: Infrastructure for Collaborative Enterprises, WET ICE 2000,
  Proceedings, IEEE 9th International Workshops, pp. 153-158 (2000)
  \bibitem{pathfinder}
  Penning H.P.: PGP pathfinder \url{pgp.cs.uu.nl}
  \bibitem{badtrust}
  Gollmann D.: Why trust is bad for security. Electronic notes in theoretical computer science, 157(3), 3-9 (2006)
  \bibitem{beaver}
  Soska K., Kwon A., Christin N., Devadas S.: Beaver: A Decentralized Anonymous Marketplace with Secure Reputation (2016)
  \bibitem{dionyziz}
  Zindros D. S.: Trust in Decentralized Anonymous Marketplaces (2015)
  \bibitem{davis}
  DeFigueiredo D. D. B., Barr E. T.: TrustDavis: A Non-Exploitable Online Reputation System. CEC, Vol. 5, pp. 274-283
  (2005)
  \bibitem{iou}
  Fugger R.: Money as IOUs in Social Trust Networks \& A Proposal for a Decentralized Currency Network Protocol.
  \url{http://archive.ripple-project.org/decentralizedcurrency.pdf} (2004)
  \bibitem{ripple}
  Schwartz D., Youngs N., Britto, A.: The Ripple protocol consensus algorithm. Ripple Labs Inc White Paper, 5 (2014)
  \bibitem{stellar}
  Mazieres, D.: The stellar consensus protocol: A federated model for internet-level consensus. Stellar Development
  Foundation (2015)
  \bibitem{deanonymisation}
  Narayanan A., Shmatikov V.: De-anonymizing Social Networks. Proceedings of the 2009 30th IEEE Symposium on Security and
  Privacy, pp. 173-187, 10.1109/SP.2009.22 (2009)
  \bibitem{silentwhispers}
  Malavolta G., Moreno-Sanchez P., Kate A.,  Maffei M.: SilentWhispers: Enforcing Security and Privacy in Decentralized
  Credit Networks (2016)
  \bibitem{privpay}
  Moreno-Sanchez P., Kate A., Maffei M., Pecina K.: Privacy preserving payments in credit networks. Network and
  Distributed Security Symposium (2015)
  \bibitem{synereo}
  Konforty D., Adam Y., Estrada D., Meredith L. G.: Synereo: The Decentralized and Distributed Social Network (2015)
  \ifdefined\proceedings
  \else
    \bibitem{amo}
    Ahuja R. K., Magnanti T. L., Orlin J. B.: Network Flows: Theory, Algorithms, and Applications. Prentice-Hall
    \url{https://ocw.mit.edu}. License: Creative Commons BY-NC-SA. (1993)
    \bibitem{jib}
    J\o{}sang A., Ismail R., Boyd C.: A Survey of Trust and Reputation Systems for Online Service Provision. Decision Support
    Systems, 43(2), pp. 618-644 (2007)
  \fi
\end{thebibliography}

