\section{Mechanics}
  We will now trace $Alice$'s steps from joining the network up to successfully completing a purchase. Suppose that initially
  all her coins, say $10\bitcoin$, are stored in such a way that she exclusively can spend them.

  Two trustworthy friends, say $Bob$ and $Charlie$, persuade her to try out Trust Is Risk. She installs the Trust Is Risk
  wallet and migrates the $10\bitcoin$ from her regular wallet, entrusting $2\bitcoin$ to $Bob$ and $5\bitcoin$ to $Charlie$.
  She now exclusively controls $3\bitcoin$ and is risking $7\bitcoin$ in exchange for being part of the network. She has full
  but not exclusive access to the $7\bitcoin$ entrusted to her friends and exclusive access to the remaining $3\bitcoin$, for
  a total of $10\bitcoin$.

  A few days later, she discovers an online shoes shop owned by $Dean$ who has also joined Trust Is Risk. She finds a nice
  pair of shoes that costs $1\bitcoin$ and checks $Dean$'s trustworthiness through her new wallet. Suppose that $Dean$ is
  deemed trustworthy up to $4\bitcoin$. Since $1\bitcoin$ is less than $4\bitcoin$, she confidently proceeds to purchase the
  shoes by paying through her new wallet.

  She can then see in her wallet that her exclusive coins have increased to $6\bitcoin$, the coins entrusted to $Bob$ and
  $Charlie$ have been reduced to $0.5\bitcoin$ and $2.5\bitcoin$ respectively and $Dean$ is entrusted $1\bitcoin$, equal to
  the value of the shoes. Also, her purchase is marked as pending. If she proceeds to check her trust towards $Dean$, it will
  again be $4\bitcoin$. Under the hood, her wallet redistributed her entrusted coins in a way that ensures that $Dean$ is
  directly entrusted with coins equal to the value of the purchased item and that her reported trust towards him has remained
  constant.

  Eventually all goes well and the shoes reach $Alice$. $Dean$ chooses to redeem $Alice$'s entrusted coins, so her wallet
  does not show any coins entrusted to $Dean$. Through her wallet, she marks the purchase as successful. This lets the system
  replenish the reduced trust to $Bob$ and $Charlie$, setting the entrusted coins to $2\bitcoin$ and $5\bitcoin$ respectively
  once more. $Alice$ now exclusively owns $2\bitcoin$. Thus, she can now use a total of $9\bitcoin$, which is expected, since
  she had to pay $1\bitcoin$ for the shoes.
