\subsection{Centrality}
  Another important measure is the graph centrality. Intuitively, a graph that resembles a mesh is preferable over a
  graph with a central hub that acts as an intermediary between all other pairs of nodes. This is because in the latter case
  Trust Is Risk does not offer any realistic improvement over the existing centralized marketplaces model (e.g. ebay).
  Nevertheless, the expected indirect trust measure is not always able to distinguish between the two. We thus propose here
  some different measures to that end.
  
  \subsubsection{Degree Centrality} \ \\

    One possible approach is the degree centrality \cite{freeman}, that can be broken down as in-degree and out-degree
    centrality. We first define the node in-degree centrality\footnote{Maybe indirect trust is more intuitive than direct
    trust in the following definition.}. Suppose that we are interested only on the induced subgraph containing players
    $\mathcal{V}' \subset \mathcal{V}$, namely $\mathcal{G}' = \mathcal{G} \setminus \left(\mathcal{V} \setminus
    \mathcal{V}'\right)$. (Note that if $\mathcal{V}' = \mathcal{V}$ then $\mathcal{G}' = \mathcal{G}$).
    \begin{align*}
      C^d_{\mathcal{G}', in}\left(A\right) = \sum\limits_{B \in \mathcal{V}' \setminus \{A\}}DTr_{B \rightarrow A} && \mbox{
      (Node in-degree centrality)}
    \end{align*}
    Let $A^*$ be the player with the maximum centrality: $A^* = \argmax\limits_{A \in \mathcal{V}'}C^d_{\mathcal{G}',
    in}\left(A\right)$.  The graph in-degree centrality is defined as:
    \begin{align*}
      C^d_{\mathcal{G}', in} = \sum\limits_{A \in \mathcal{V}'}\left(C^d_{\mathcal{G}', in}\left(A^*\right) -
      C^d_{\mathcal{G}', in}\left(A\right)\right) && \mbox{ (Graph in-degree centrality)}
    \end{align*}
    \addtocounter{footnote}{-1}
    Similarly, for the out-degree centrality we have\footnotemark:
    \begin{align*}
      C^d_{\mathcal{G}', out}\left(A\right) = \sum\limits_{B \in \mathcal{V}' \setminus \{A\}}DTr_{A \rightarrow B} && \mbox{
      (Node out-degree centrality)}
    \end{align*}
    Let $A^* = \argmax\limits_{A \in \mathcal{V}'}C^d_{\mathcal{G}', out}\left(A\right)$. The graph out-degree centrality is:
    \begin{equation*}
      C^d_{\mathcal{G}', out} = \sum\limits_{A \in \mathcal{V}'}\left(C^d_{\mathcal{G}', out}\left(A^*\right) -
      C^d_{\mathcal{G}', out}\left(A\right)\right) \mbox{ (Graph out-degree centrality)}
    \end{equation*}

    A problem of these centrality measures is that their unit is the currency used (i.e. Bitcoin) and thus may not always have
    an intuitive meaning. We would thus like to have a measure of \textit{centralization} that has no units and can take
    values in the interval $\left[0,1\right]$, with 0 corresponding to a graph of no centralization (all nodes are equal,
    e.g.  cycle) and 1 to a graph with the maximum centralization possible (there is one central vital node for all, e.g.
    star). A centralization measure that achieves this target is proposed in \cite{freeman}. Here we use the following
    modified form. For an induced subgraph $\mathcal{G}'$, the in- and out-centralization are defined as:
    \begin{align*}
      Cn^d_{\mathcal{G}', in} &= \frac{C^d_{\mathcal{G}', in}}{\max C^d_{\mathcal{G}', in}} && \mbox{ (in-degree
      centralization)} \\
      Cn^d_{\mathcal{G}', out} &= \frac{C^d_{\mathcal{G}', out}}{\max C^d_{\mathcal{G}', out}} && \mbox{ (out-degree
      centralization)} \enspace,
    \end{align*}
    where $\max C^d_{\mathcal{G}', in}$ is defined as the maximum in-degree centrality over all graphs with the same number of
    nodes, for which the total incoming direct\footnote{Maybe indirect trust is more intuitive here than direct trust.} trust
    of each node is equal to the total incoming \addtocounter{footnote}{-1}direct\footnotemark \ trust of the corresponding
    node in $\mathcal{G}'$. $\max C^d_{\mathcal{G}', out}$ is defined equivalently. Please note that the aforementioned graphs
    are always well defined.

  \subsubsection{maxFlow Centrality} \ \\

    An alternative measure of centrality for a player $A \in \mathcal{V}' \subset \mathcal{V}$ of an induced subgraph
    $\mathcal{G}' = \mathcal{G} \setminus \left(\mathcal{V} \setminus \mathcal{V}'\right)$ can be defined as the impact that
    the removal of $A$ would have on the indirect trust between the rest of the players on $\mathcal{G}'$. More specifically,
    let $\mathcal{G}'' = \mathcal{G}' \setminus \{A\}$. Then it is:
    \begin{align*}
      C^{mF}_{\mathcal{G}'}\left(A\right) = \sum\limits_{B,C \in \mathcal{V}''}\left(Tr_{\mathcal{G}', B \rightarrow C} -
      Tr_{\mathcal{G}'', B \rightarrow C}\right) && \mbox{ (Node maxFlow centrality)} \enspace.
    \end{align*}
    We can now follow the same steps as previously for the relevant graph definitions. Let $A^* = \argmax\limits_{A \in
    \mathcal{V}'}C^{mF}_{\mathcal{G}'}\left(A\right)$. Then the graph maxFlow centrality is:
    \begin{align*}
      C^{mF}_{\mathcal{G}'} = \sum\limits_{A \in \mathcal{V}'}\left(C^{mF}_{\mathcal{G}'}\left(A^*\right) -
      C^{mF}_{\mathcal{G}'}\left(A\right)\right) && \mbox{ (Graph maxFlow centrality)}
    \end{align*}
    and the centralization:
    \begin{align*}
      Cn^{mF}_{\mathcal{G}'} = \frac{C^{mF}_{\mathcal{G}'}}{\max C^{mF}_{\mathcal{G}'}} && \mbox{ (Graph maxFlow
      centralization)} \enspace,
    \end{align*}
    where $\max C^{mF}_{\mathcal{G}'}$ is the maximum centrality over all graphs with the same number of nodes, for which the
    total incoming and outgoing direct\footnote{Maybe indirect trust is more intuitive here than direct trust.} trusts of each
    node are equal to the total incoming and outgoing \addtocounter{footnote}{-1} direct\footnotemark \ trusts of the
    corresponding node $\mathcal{G}'$, except for $A^*$, which corresponds to the central node whose incoming and outgoing
    direct trusts are defined by those of the rest of the nodes. Please note that the aforementioned graph is always well
    defined.
