\subsection{Buyers, Sellers, Middlemen}
  Buyers only desire to buy products and do not have incoming trust. Sellers only desire to accumulate capital through selling
  products and do not have outgoing trust. Middlemen desire to accumulate capital as well and are allowed to have both
  incoming and outgoing trust. Their utility stems only from in-game factors. A more thorough description follows:

  \begin{itemize}
    \item \textit{Buyers}

    Buyers initially are provided only with outgoing direct trust towards sellers and middlemen, no Capital or incoming direct
    trust. They cannot reallocate their outgoing direct trust, only complete purchases of the product from sellers that are
    trustworthy enough.
    
    To pay for a product, they use the linear program defined in thesis.pdf to aquire the funds needed and directly entrust
    the necessary part of these funds to the seller. Sellers are supposed to complete their part of the exchange within a
    constant amount of rounds, $r$. If the product has arrived after $r$ rounds, the remaining funds are reallocated to the
    players from whom they were taken in proportional fashion.The way they are reallocated ensures that
    \begin{equation*}
      \forall B \in \mathcal{S}_1, \frac{DTr_{Buyer \rightarrow B, i}}{\sum\limits_{C \in \mathcal{S}_1}DTr_{Buyer \rightarrow
      C, i}} = \frac{DTr_{Buyer \rightarrow B, i + r}}{\sum\limits_{C \in \mathcal{S}_1}DTr_{Buyer \rightarrow C, i + r}}
      \enspace,
    \end{equation*}
    where $S_1$ is the set of players from whom the buyer reduced her direct trust to initiate the purchase (this set may also
    contain the seller).

    If the product does not arrive after $r$ rounds, the direct trust to the seller is withdrawn (if it is still available)
    and all the funds involved (both the price and the surplus funds removed because of the linear program) are reallocated as
    direct trusts towards the rest of the players in a proportional fashion. The way they are reallocated ensures that
    \begin{equation*}
      \forall B \in \mathcal{S}_2, \frac{DTr_{Buyer \rightarrow B, i}}{\sum\limits_{C \in \mathcal{S}_2}DTr_{Buyer \rightarrow
      C, i}} = \frac{DTr_{Buyer \rightarrow B, i + r}}{\sum\limits_{C \in \mathcal{S}_2}DTr_{Buyer \rightarrow C, i + r}}
      \enspace,
    \end{equation*}
    where $S_2 = \left(\mathcal{V} \setminus \mathcal{S}_1\right) \setminus{\{Buyer, Seller\}}$.
    \item \textit{Sellers}

    \item \textit{Middlemen}

    dsof
  \end{itemize}
