\subsection{Random Roles}
  All players follow the same strategy, according to which each player is permitted to freely add or steal direct trust from
  other players. After $R$ rounds (blocks in bitcoin terms) exactly two players are selected at random (these choices follow
  the uniform distribution). One is dubbed seller and the other buyer. The seller offers a good that costs $C$, which she
  values at $C - l$ and the buyer values at $C + l$. The values $R, C$ and $l$, as well as the uniform distribution with which
  the buyer and seller are chosen, are common knowledge from the beginning of the game. The exchange completes if and only if
  $DTr_{Buyer \rightarrow Seller} \geq C$. There are three variants of the game, each with a different utility for the
  players (the first two versions have two subvariants each):

  \begin{enumerate}
    \item If player $A$ is not chosen to be either buyer or seller, then her utility is equal to $Cap_{A, R}$. Intuitively
    players do not attach any value to having (incoming or outgoing) direct trust at the end of the game. If the buyer and the
    seller do not manage to complete the exchange, the buyer's utility is $Cap_{Buyer, R}$. If on the other hand they manage
    to exchange the good, then the buyer's utility is $Cap_{Buyer, R} + l$. Intuitively these utilities signify that the buyer
    uses her preexisting Capital to buy. As for the seller there exist two subvariants for her utility:
    \begin{enumerate}
      \item If the exchange is not completed, the seller's utility is $Cap_{Seller, R} - l$. If the exchange takes place, the
      seller's utility is $Cap_{Seller, R}$. Intuitively, the seller is first obliged to buy the good from the environment at
      the cost of $C$.

      \item If the exchange is not completed, the seller's utility is $Cap_{Seller, R} + C - l$. If the exchange takes place, the
      seller's utility is $Cap_{Seller, R} + C$. Intuitively, the seller is handed the good for free by the environment.
    \end{enumerate}
    
    \item If player $A$ is not chosen to be either buyer or seller, then her utility is equal to $\sum\limits_{\overset{B \in
    \mathcal{V}}{B \neq A}}\left(DTr_{A \rightarrow B, R} + DTr_{B \rightarrow A, R}\right) + Cap_{A, R}$. Intuitively players
    attach equal value to all the funds they can directly spend, regardless of whether others can spend them as well. If the
    buyer and the seller do not manage to complete the exchange, the buyer's utility is $\sum\limits_{\overset{B \in
    \mathcal{V}}{B \neq Buyer}}\left(DTr_{Buyer \rightarrow B, R} + DTr_{B \rightarrow Buyer, R}\right) + Cap_{Buyer, R}$. If
    on the other hand they manage to exchange the good, then the buyer's utility is $\sum\limits_{\overset{B \in
    \mathcal{V}}{B \neq Buyer}}\left(DTr_{Buyer \rightarrow B, R} + DTr_{B \rightarrow Buyer, R}\right) + Cap_{Buyer, R} + l$.
    Intuitively these utilities signify that the buyer uses her preexisting accessible funds to buy. As for the seller there
    exist two subvariants for her utility:
    \begin{enumerate}
      \item If the exchange is not completed, the seller's utility is $\sum\limits_{\overset{B \in \mathcal{V}}{B \neq
      Seller}}\left(DTr_{Seller \rightarrow B, R} + DTr_{B \rightarrow Seller, R}\right) + Cap_{Seller, R} - l$. If the
      exchange takes place, the seller's utility is $\sum\limits_{\overset{B \in \mathcal{V}}{B \neq Seller}}\left(DTr_{Seller
      \rightarrow B, R} + DTr_{B \rightarrow Seller, R}\right) + Cap_{Seller, R}$. Intuitively, the seller is first obliged to
      buy the good from the environment at the cost of $C$.

      \item If the exchange is not completed, the seller's utility is $\sum\limits_{\overset{B \in \mathcal{V}}{B \neq
      Seller}}\left(DTr_{Seller \rightarrow B, R} + DTr_{B \rightarrow Seller, R}\right) + Cap_{Seller, R} + C - l$. If the
      exchange takes place, the seller's utility is $\sum\limits_{\overset{B \in \mathcal{V}}{B \neq Seller}}\left(DTr_{Seller
      \rightarrow B, R} + DTr_{B \rightarrow Seller, R}\right) + Cap_{Seller, R} + C$. Intuitively, the seller is handed the
      good for free by the environment.
    \end{enumerate}


    \item If player $A$ is not chosen to be either buyer or seller, then her utility is 0. If the buyer and the seller do not
    manage to complete the exchange, their utility is 0 as well. If on the other hand they manage to exchange the good, then
    the utility is $l$ for both of them. Intuitively these utilities signify that in this game there is gain only for those
    who exchange goods and the gain is exactly the difference between the objective value and the subjective value that the
    relevant parties perceive.
  \end{enumerate}

