\section{Centrality}
  Another important measure is the network centrality. We propose here some different measures to that end.
  
  \subsection{Degree Centrality} \

    One possible approach is the degree centrality [Freeman citation], that can be broken down as in-degree and out-degree
    centrality. We first define the node in-degree centrality.
    \begin{equation*}
      C_{in}\left(A\right) = \sum\limits_{B \in \mathcal{V} \setminus \{A\}}DTr_{B \rightarrow A}\footnote{Maybe indirect
      trust is more intuitive here than direct trust.} \mbox{ (Node in-degree centrality)}
    \end{equation*}
    Let $A^* = \argmax\limits_{A \in \mathcal{V}}C_{in}\left(A\right)$. The network in-degree centrality is defined as:
    \begin{equation*}
      C_{in} = \sum\limits_{A \in \mathcal{V}}\left(C_{in}\left(A^*\right) - C_{in}\left(A\right)\right) \mbox{ (Network
      in-degree centrality)}
    \end{equation*}
    Similarly, for the out-degree centrality we have:
    \addtocounter{footnote}{-1}
    \begin{equation*}
      C_{out}\left(A\right) = \sum\limits_{B \in \mathcal{V} \setminus \{A\}}DTr_{A \rightarrow B}\footnotemark \mbox{ (Node
      out-degree centrality)}
    \end{equation*}
    Let $A^* = \argmax\limits_{A \in \mathcal{V}}C_{out}\left(A\right)$. The network out-degree centrality is defined as:
    \begin{equation*}
      C_{out} = \sum\limits_{A \in \mathcal{V}}\left(C_{out}\left(A^*\right) - C_{out}\left(A\right)\right) \mbox{ (Network
      out-degree centrality)}
    \end{equation*}

    A problem of these centrality measures is that their unit is the currency used (i.e. Bitcoin) and thus may not always have
    an intuitive meaning. We would thus like to have a measure of \textit{centalization} that has no units and can take values
    in the interval $\left[0,1\right]$, with 0 corresponding to a network of no centralization (all nodes are equal, e.g.
    cycle) and 1 to a network with the maximum centralization possible (there is one central vital node for all, e.g. star). A
    centralization measure that achieves this target is proposed in [Freeman citation]. Here we use the following modified
    form. For a graph $\mathcal{G}$, the in- and out-centralization are defined as:
    \begin{equation*}
      C'_{in} = \frac{C_{in}}{\max C_{in}} \: \mbox{ and } \: C'_{out} = \frac{C_{out}}{\max C_{out}} \enspace,
    \end{equation*}
    where $\max C_{in}$ is defined as the maximum in-degree centrality for any graph with the same number of nodes for which
    the maximum direct\footnote{Maybe indirect trust is more intuitive here than direct trust.} trust is equal to the maximum
    \addtocounter{footnote}{-1} direct\footnotemark direct trust of $\mathcal{G}$. $\max C_{out}$ is defined equivalently.

    \noindent\hrulefill
    \newpage
